Men and Women Both Prefer and Perceive Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
paper update

This report takes the data from the Study 2 from “Evaluations of Action and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes: Inaction Agents Are Preferred to and Perceived as More Competent and Normative Than Action Agents” to examine if there are differences in moral judgment between gender. The estimands of interest from the data set are preference and perceived competence between action and inaction agents by gender. Data was taken from the *Center for Open Science* and published directly by Fillion, Strauch, and Feldman. To examine whether or not there are differences in preferences and perceived competence of different decision-making actions between gender, graphical analysis was conducted to visualize the responses of study participants. Summary statistics were calculated to discern if the differences in responses were of statistical significance. Report findings reveal that there are no statistical differences in the preference and perceived competence between gender which could indicate that there are other factors aside from gender that influence moral judgment preferences.

The Data section of this report aims to discuss the characteristics of the Study 2 data set used in addition to the methods of cleaning applied to get workable data for this report. This report’s Results section highlights trends discovered through graphical analysis in tandem with statistical analysis of the preference and perceived competence responses using t-tests and p-values to determine statistical insignificance. The Discussion section notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. Specific discussion will surround the validity of assigning utilitarianism as a trait of men in addition to addressing whether or not there are differences in decision-making approaches based on gender. To summarize the report’s content, the Conclusion section briefly touches on the overall insights on moral judgment and gender that can be distilled from the findings of this report.

>>>>

This report takes the data from the Study 2 from “Evaluations of Action and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes: Inaction Agents Are Preferred to and Perceived as More Competent and Normative Than Action Agents” to examine if there are differences in moral judgment between gender. The estimands of interest from the data set are preference and perceived competence between action and inaction agents by gender. To examine whether or not there are differences in preferences and perceived competence of different decision-making actions between gender, graphical analysis was conducted to visualize the responses of study participants. Summary statistics were calculated to discern if the differences in responses were of statistical significance. Report findings reveal that there are no statistical differences in the preference and perceived competence between gender which could indicate that there are other factors aside from gender that influence moral judgment preferences.

The Data section of this report aims to discuss the characteristics of the Study 2 data set examined in addition to the methods of cleaning applied to get workable data for this report. This report’s Results section highlights trends discovered through graphical analysis in tandem with statistical analysis of the preference and perceived competence responses using t-tests and p-values to determine statistical insignificance. The Discussion section notes possible analytical limitations and measurement errors in the data sets in addition to overall insights of the report’s analysis. Specific discussion will surround the validity of assigning utilitarianism as a trait of men in addition to addressing whether or not there are differences in decision-making approaches based on gender. To summarize the report’s content, the Conclusion section briefly touches on the overall insights on moral judgment and gender that can be distilled from the findings of this report.
